The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-05-14 RET_Hosts_CWR.tex
Updates from Overleaf

@@

To show how RETs compare to the galaxy population as a whole, we use the MPA-JHU catalogues of stellar masses (based on the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}). The mean redshift is 0.08 which is much lower than for the RETs, such that significant evolution in the galaxy population has happened between the majority of RET hosts and the SDSS sample. We do not correct for this, but take it into account when analysing our findings. 
\section{Host galaxy observations}
\label{sec:obs}
\subsection{Photometry \label{subsec:phot}}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
\caption{The $M_*$ - SFR sequence of RET hosts, hosts of other transients, and SDSS field galaxies (grey contours). SFRs have not been corrected for redshift evolution. RET hosts lie slightly above the low-$z$ star-formation main sequence \replyrick{upper half of the SDSS contours}, and systematically avoid passive galaxies (dense SDSS contours in the lower right).
\label{fig:sfms_sfr}}
\end{figure}

%\begin{figure}
%\includegraphics[width=0.5\textwidth]{figs/cum_SFR_mike.png}
%\caption{Cumulative distributions of the SFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
%\label{fig:sfr_cum}}
%\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
\caption{The $M_*$ - sSFR sequence of RET hosts and comparison samples, along with the SDSS field galaxies.
\label{fig:sfms_ssfr}}
\end{figure}

@@

\subsection{Star formation rate \label{subsec:res_sfr}}
Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS. RETs follow CCSNe, LGRBs and SLSNe in avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars. One object (DES16C1cbd) lies among passive galaxies. The spectrum of this object is red in colour, but does exhibit \OII~emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar. The \replyrick{hosts of} individual rapid transients Cow, Koala and SN2018gep are lower in mass than the majority of RETs. SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs. SNLS04D4ec is consistent with the peak of the DES RET mass and SFR distributions.

Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency. It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR. Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments \replyrick{of} LGRBs or SLSNe.

>>>>

\subsection{The DES supernova programme \label{subsec:desdata}}

\replyrick{The Dark Energy Survey (DES) makes use of the Dark Energy Camera (DECam; \citealt{Flaugher2015}) to survey $5000\deg^2$ of the southern sky between 2013 and 2019. The supernova programme (DES-SN), designed primarily to perform cosmology with type Ia SNe \citep{Bernstein2012}, consisted of five 6-month seasons of approximately 7 day cadence \citep{DAndrea2018}} in ten single pointings, known as the SN fields. Of these fields, two were observed with longer exposure times and are referred to as deep fields; the remaining eight are labelled shallow. Transient detection was performed by difference imaging using a custom pipeline \citep{Kessler2015}. Transient candidates were vetted via machine-learning techniques \citep{Goldstein2015}, leading to $\sim 30,000$ viable supernova candidates over the full five seasons. A full description of the search for rapid transients in DES can be found in \citetalias{Pursiainen2018}.

@@

To show how RETs compare to the galaxy population as a whole, we use \replyrick{a sample of $\sim800,000$ measurements from the} MPA-JHU catalogues of stellar masses (based on the methods of \citealt{Kauffmann2003,Salim2007}), SFRs (based off \citealt{Brinchmann2004}), and metallicities (based off \citealt{Tremonti2004}) from the  catalogues of SDSS Data Relase 7 (DR7; \citealt{Abazajian2009}). The mean redshift is 0.08 which is much lower than for the RETs, such that significant evolution in the galaxy population has happened between the majority of RET hosts and the SDSS sample. We do not correct for this, but take it into account when analysing our findings. 
\section{Host galaxy observations}
\label{sec:obs}
\subsection{Photometry \label{subsec:phot}}

@@

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_RETs.png}
\caption{The $M_* -$ SFR sequence of RET hosts, hosts of other rapid transients and SNe II, and SDSS field galaxies (grey contours). SFRs have not been corrected for redshift evolution. RET hosts lie slightly above the low-$z$ star-formation main sequence \replyrick{upper half of the SDSS contours}, and systematically avoid passive galaxies (dense SDSS contours in the lower right).
\label{fig:sfms_sfr}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/SFR_Mike_Other.png}
\caption{Same as Fig. \ref{fig:sfms_sfr}, but comparing RET hosts with hosts of SESNe, LGRBs and SLSNe, and SDSS field galaxies (grey contours).
\label{fig:sfms_sfr_other}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_RETs.png}
\caption{The $M_* -$ sSFR sequence of RET hosts as well as local rapid transients and SNe II, along with the SDSS field galaxies.
\label{fig:sfms_ssfr}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike_other.png}
\caption{Same as Fig. \ref{fig:sfms_ssfr} but comparing RET hosts with hosts of SESN, LGRB, and SLSN hosts, along with the SDSS field galaxies.
\label{fig:sfms_ssfr_other}}
\end{figure}

@@

\subsection{Star formation rate \label{subsec:res_sfr}}
Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_sfr_other}, \replyrick{split in two for clarity,} show the `star formation main sequence' (SFMS) of RET host galaxies, as determined from photometric SED fitting along with that for the comparison samples and for the field galaxies of SDSS. RETs follow CCSNe, LGRBs and SLSNe in avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars. One object (DES16C1cbd) lies among passive galaxies. The spectrum of this object is red in colour, but does exhibit \OII~emission indicative of recent star-formation activity consistent with the upper end of the sSFR error bar. The \replyrick{hosts of} individual rapid transients Cow, Koala and SN2018gep are lower in mass than the majority of RETs. SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs. SNLS04D4ec is consistent with the peak of the DES RET mass and SFR distributions.

Figs.~\ref{fig:sfms_ssfr} and \ref{fig:sfms_ssfr_other} are similar to Figs.~\ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr_other}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is a more representative measure of the star-forming efficiency. It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies in terms of sSFR. Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely star-forming environments \replyrick{of} LGRBs or SLSNe.
